### 2020-04-07 Supplement_forPNAS.Rmd
SHDH final comments and error proofing

---
bibliography: manuscript.bib
csl: pnas.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
indent: TRUE
monofont: "Times New Roman"
fontsize: 12pt
language:
  label:
    fig: "**Figure S**"
    tab: "**Table S**"
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \doublespacing
---

@@

Alejandro Damian-Serrano, Steven H.D. Haddock, Casey W. Dunn

@@

Diet data curation: We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp. eating *Aegina* since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores. Personal observations on feeding (from SHDH, CAC, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*. The feeding guilds declared in this study are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group). These were selected to minimize the number of categories while keeping the most different types of prey separate.

@@

Other trees inferred in this work include:

@@

The constrained tree inferences utilized the following constrain topology:

@@

DAPC discriminant analyses:

@@

Ordinary and phylogenetic logistic regression of morphological characters and the presence/absence of prey types:

@@

Variance-Covariance Matrix analyses of phenotypic intergation and evolutionary modularity:

@@

![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the whole tree covariance matrix.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs.png){height=600px}

![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in \@ref{VCV_regimes} and the covariance matrices in their preceding regime, the large-crustacean specialist regime.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs_anc.png)

@@

>>>>

---
bibliography: manuscript.bib
csl: pnas.csl
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_document2:
    toc: FALSE
indent: TRUE
monofont: "Times New Roman"
fontsize: 12pt
language:
  label:
    fig: "**Figure S**"
    tab: "**Table S**"
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage{placeins}
---

@@

@@

Diet data curation: We removed the gelatinous prey observations for *Praya dubia* eating a ctenophore and a hydromedusa, and for *Nanomia* sp. eating *Aegina* since we believe these are rare events that have a much larger probability of being detected by ROV methods than their usual prey, and it is not clear whether the medusae were attempting to prey upon the siphonophores. Personal observations on feeding (from SHDH, Anela Choy, and Philip Pugh) were also included for *Resomia ornicephala*, *Lychnagalma utricularia*, *Bargmannia amoena*, *Erenna richardi*, *Erenna laciniata*, *Erenna sirena*, and *Apolemia rubriversa*. The feeding guilds declared in this study are: small-crustacean specialist (feeding mainly on copepods and ostracods), large crustacean specialist (feeding on large decapods, mysids, or krill), fish specialist (feeding mainly on actinopterygian larvae, juveniles, or adults), gelatinous specialist (feeding mainly on other siphonophores, medusae, ctenophores, salps, and/or doliolids), and generalist (feeding on a combination of the aforementioned taxa, without favoring any one prey group). These were selected to minimize the number of categories while keeping the most different types of prey separate.

@@

@@

@@

@@

@@

@@

![\label{VCV_diffs} Scaled differences between the regime-specific covariance matrices in S21 and the whole tree covariance matrix.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs.png){height=600px}

![\label{VCV_diffs_anc} Scaled differences between the regime-specific covariance matrices in S21 and the covariance matrices in their preceding regime, the large-crustacean specialist regime.](Supplementary_materials/Online_appendices/PNGs/VCVdiffs_anc.png)

@@

\FloatBarrier
